%-----------------------------------------
% Seth Reno
% Resumé
%
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}
\moderncvtheme[darkblue]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[utf8]{inputenc}
\defaultfontfeatures{Mapping=tex-text}

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco} 

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR


% Personal Information
\firstname{Seth}
\familyname{Reno}
\mobile{(816) 352-6684}
\email{sethreno@gmail.com}
\homepage{github.com/sethreno}

\title{Seth Reno's Resume}

\nopagenumbers{}

\begin{document}
\maketitle
\section{Summary}
\cvline{}{ 
I am a software development leader who cares about my craft and strives to make
software people use and love. I have a passion for learning and sharing
knowledge. I use this to bring the state of the art to the state of the
industry.
}

\section{Languages \& Tools} 
	\cvline {Languages:}
{C\#, JavaScript, Python, Java, VB.NET, C, Ruby, Scheme, SQL, HTML, CSS, shell scripting}
	\cvline {Frameworks:}
{.NET Core, ASP.NET, Nancy, React, WPF, Django, Ruby on Rails}
	\cvline {Software:}
{Vim, VS Code, Git, Docker, Jenkins, IIS, SQL Server, PostgreSQL, Redis, RabbitMQ }

\section{Experience} 
	\cventry
{2012 -- Now} {Technical Lead}{Rosnet}{Parkville, MO}{}{
		\begin{itemize}
			\item
				Filled a dev ops role by setting up and maintaining
				automated builds, deployments, cross platform code
				search, SQL server version control, Bitbucket, \& Jira.
			\item
				Designed and implemented Rosnet's POS integration
				platform. This system has clients running on thousands of
				machines and integrates 25 different POS systems with
				Rosnet. It provides near real-time data and services
				\char`\~5,000 requests per minute.
			\item
				Designed and implemented Rosnet's public API.
				\httplink{api.rosnet.com}
			\item
				Designed and implemented a labor rules engine which
				calculates pay for thousands of employees daily.
			\item
				Designed and implemented the framework for Rosnet's next
				generation Food Management system.
		\end{itemize}
}
	\cventry
{2019 -- Now} {Lead Maintainer}{ReGitLint}{github.com/sethreno/ReGitLint}{}{
		\begin{itemize}
			\item 
				Created and mainted ReGitLint, an open source code formatting
				utility that helps development teams maintain consistem code
				style.
		\end{itemize}
}
	\cventry
{2009 -- Now} {Lead Maintainer}{Schema Zen}{github.com/sethreno/schemazen}{}{
		\begin{itemize}
			\item 
				Reviewed and merged contributions from developers from around the world
				with a wide range of skill levels.
			\item 
				Maintained a code base for over a decade as the underlying .net
				framework has evolved.
		\end{itemize}
}
	\cventry
{2020 -- 2021} {Consultant}{ECS Geothermal}{Smithville, MO}{}{
		\begin{itemize}
			\item 
				Designed and implemented phase 1 of a custom cloud hosted CRM
				using .NET Core, Azure App Services, \& AWS Postgres RDBMS.
		\end{itemize}
}
	\cventry
{2005 -- 2012} {Sr. Programmer Analyst}{Cameron Insurance Companies}{Cameron, MO}{}{
		\begin{itemize}
			\item 
				Completed a three year mainframe policy system
				replacement project. My role was technical lead on a
				team comprised of four .NET developers, four COBOL
				programmers, and an outside vendor. During this project
				I utilized my skills in communication, project
				management, and object oriented analysis and design to
				help provide an effective solution.
		\end{itemize}
}

	\cventry
{2001 -- 2005}{Sr. System Administrator}{Shook, Hardy, \& Bacon}{Kansas City, MO}{}{
		\begin{itemize}
			\item
				Developed various applications and scripts scripts to
				automate repetitive system administration tasks.
		\end{itemize}
	}

\section{Education} 
	\cventry
{2001 -- 2004}{Bachelor of Science in Computer Information Systems}{DeVry University}{Kansas City, MO}{}{}

\end{document}

