%-----------------------------------------
% Seth Reno
% Resumé
%
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}
\moderncvtheme[darkblue]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[utf8]{inputenc}
\defaultfontfeatures{Mapping=tex-text}

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco} 

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR


% Personal Information
\firstname{Seth}
\familyname{Reno}
\mobile{(816) 352-6684}
\email{sethreno@gmail.com}
\homepage{github.com/sethreno}

\title{Seth Reno's Resume}

\nopagenumbers{}

\begin{document}
\maketitle
\section{Summary}
\cvline{}{ 
I am a software engineer who cares about my craft and strives to make software
people enjoy using. I have proven success as an individual contributor,
architect, and team lead. I love building software and believe work should be
fun.
}

\section{Languages \& Frameworks}
	\cvline {Languages:}
		{C\#, Python, SQL, JavaScript, TypeScript, HTML, CSS, shell scripting}
\linebreak
	\cvline {Frameworks:}
		{.NET, ASP.NET, React, Django}

\section{Experience} 
	\cventry
{2025 -- Now} {Sr. DevOps Engineer IDR-TA}{Index Analytics}{Baltimore, MD}{Remote}{
		\begin{itemize}
			\item
				Implemented features, helped design, performed code reviews, and provided
				production support for the IDR-TA Rules Engine. It provides
				analysts with AI insights, workflow tools, and a chatbot to help them
				determine dispute eligibility quickly and accurately. It has a
				microservices architecture using AWS Bedrock, Python, Java
				Spring Boot, Angular (TypeScript), and Postgres for data storage.
			\item
				Proactively optimized AWS costs reducing monthly spend by 50\%.
			\item
				Implemented CI/CD pipelines using GitHub Actions and AWS CDK
				which reduced contention deploying microservices and improved
				developer productivity.
			\item
				Helped team responsibly adopt agentic coding tools by creating
				agent instructions, providing training, and ensuring settings
				comply with company and CMS policies.
			\item
				Monitored and resolved security vulnerabilites helping the
				project gain ATO in the CMS AWS environment.
			\item
				Reviewed implementation of AI QA tool built by KPMG and
				provided guidance ensuring it met performance, security, and
				reliability requirements.
		\end{itemize}
}
\linebreak

	\cventry
{2023 -- 2025} {Sr. Staff Engineer}{Rosnet}{Parkville, MO}{Remote}{
		\begin{itemize}
			\item
				Helped teams improve velocity by assisting with CI/CD,
				containerization, and observability.
			\item
				Reviewed and simplified designs for multiple projects saving the
				company hundreds of dev hours.
			\item
				Created pull request style SE interview screening process to
				help teams hire faster.
			\item
				Improved documentation and diagrams for critical legacy systems
				that were not well understood.
			\item
				Implemented framework for secure secrets management using Azure
				Key Vault.
			\item
				Discovered and resolved multiple complex security
				vulnerabilities.
		\end{itemize}
}
\linebreak

	\cventry
{2021 -- 2023} {Tech Lead}{Rosnet}{Parkville, MO}{Remote}{
		\begin{itemize}
			\item
				Bootstrapped and led a highly successful team that delivered
				multiple features using .NET, SignalR, React, RabbitMQ, \&
				Elasticsearch.
			\item
				Implemented forecasting for new menu
				items that integrates with legacy sales forecast system.
			\item
				Addressed one of the company's largest scalability issues by
				queuing expensive operations.
			\item
				Implemented production replay system used for load
				testing heavyweight SQL Server workloads.
		\end{itemize}
}
\linebreak

	\cventry
{2012 -- 2020} {Sr. Software Engineer}{Rosnet}{Parkville, MO}{}{
		\begin{itemize}
			\item
				Implemented Rosnet's data ingestion platform. This is a
				distributed system with clients running on thousands of
				machines that processes over 3TB of data daily. It integrates 30
				different POS systems with Rosnet providing near real-time data
				for reporting and analytics. This system has been the foundation
				of Rosnet's business for over a decade.
			\item
				Implemented Rosnet's public API. \httplink{api.rosnet.com}
			\item
				Implemented a labor rules engine to accurately calculate
				pay and help restaurants comply with labor laws.
				Includes an innovative test framework that allows tests
				to be written in markdown.
			\item
				Setup CI/CD pipelines for multiple projects using Jenkins.
		\end{itemize}
}
\linebreak

	\cventry
{2006 -- 2012} {Sr. Programmer Analyst}{Cameron Insurance Companies}{Cameron, MO}{}{
		\begin{itemize}
			\item 
				Technical lead on a multi-year mainframe policy system
				replacement project.
			\item 
				Wrote a business object framework which is used to enforce
				complex underwriting rules.
			\item 
				Created an ASP.NET web portal used by insurance agents to quote
				rates for insurance policies.
			\item 
				Implemented a web service that uses industry standard XML to
				provide real time rating services to third party comparative
				raters.
			\item
				Advocated for and helped team adopt automated testing
				and database version control.
		\end{itemize}
}
\linebreak

	\cventry
{2005 -- 2006} {Programmer Analyst}{Cameron Insurance Companies}{Cameron, MO}{}{
		\begin{itemize}
			\item
				Implemented policy declarations printing system using .NET framework.
				Completed this project in a fraction of the time expected by
				parsing legacy COBOL programs which contained the x and y
				coordinates of each form field.
			\item
				Implemented native app that allowed insurance adjusters
				to upload images efficiently from low bandwidth internet
				connections.
		\end{itemize}
}
\linebreak

	\cventry
{2001 -- 2005}{Sr. System Administrator}{Shook, Hardy, \& Bacon}{Kansas City, MO}{}{
		\begin{itemize}
			\item
				Developed an application that tracks hardware, software, and
				drive usage on 250 servers.
			\item
				Developed various applications and scripts to automate
				repetitive system administration tasks.
		\end{itemize}
}
\linebreak

\section{Freelance, Open Source, \& Side Projects} 
	\cventry
{2024 -- Now} {Side Project}{Budget Flow}{\httplink{budgetflow.io}}{}{
		\begin{itemize}
			\item 
				Created a web app to make it easier to track spending by
				category and see cash flow projections. Uses React (Refine),
				Supabase, Python, scikit-learn, \& Cloudflare.
		\end{itemize}
}
\linebreak

	\cventry
{2009 -- 2025 } {Open Source}{Schema Zen}{\httplink{github.com/sethreno/schemazen}}{336 stars}{
		\begin{itemize}
			\item 
				Created a tool to dump and restore SQL Server schema to text
				files for version control. This tool is preferred by many over
				similar solutions from Microsoft and Redgate due to it's speed
				and simplicity.
			\item 
				Includes regression tests that create, dump, \& compare
				databases using the tool against SQL Server Docker images in
				GitHub Actions.
			\item 
				Reviewed and merged contributions from developers from around the world
				with a wide range of skill levels.
			\item 
				Maintained a code base for over a decade as the underlying .NET
				framework has evolved.
		\end{itemize}
}
\linebreak


\section{Education \& Certifications} 
	\cventry
{2001 -- 2004}{Bachelor of Science in Computer Information Systems}{DeVry University}{Kansas City, MO}{}{}
	\cventry
{2025}{AWS Certified Cloud Practitioner}{}{}{}{}

\end{document}

